The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
Added funding for Marc Fehling.

W.~Bangerth was also partially supported by Award OAC-1835673 as part of
the Cyberinfrastructure for Sustained Scientific Innovation (CSSI) program,
DMS-1821210, and EAR-1925595.

>>>>

W.~Bangerth and M.~Fehling were partially supported by Award OAC-1835673
as part of the Cyberinfrastructure for Sustained Scientific Innovation (CSSI)
program.

W.~Bangerth was also partially supported by Awards DMS-1821210 and EAR-1925595.
